\documentclass[sigconf]{acmart}

\usepackage{enumitem}
\usepackage{framed}
\usepackage[11pt]{moresize}
\usepackage{cprotect}
\usepackage{enumitem}
\usepackage{listings}
\usepackage{amstext}
\usepackage{amstext}
\usepackage{pdfpages}
\usepackage{alltt}
\usepackage{epstopdf}
\usepackage{xspace,colortbl}
\usepackage[USenglish]{babel}
\usepackage{multirow}
\usepackage{url}
\usepackage{graphicx}%%
\usepackage{amssymb}
\usepackage{fmtcount}
\usepackage{amsfonts}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage[mathscr]{eucal}
%\usepackage{psfrag}
\usepackage{colortbl}
\usepackage{times}


\usepackage{bm}
%\usepackage[nospace]{cite}
\usepackage{csquotes}
\usepackage{enumitem}

\lstset{basicstyle=\small,breaklines=true,language=Python,belowcaptionskip=.1\baselineskip}

\usepackage{balance}

%\linespread{0.99}

\copyrightyear{2017} 
\acmYear{2017} 
\setcopyright{acmcopyright}
\acmConference{HILDA'17}{May 14, 2017}{Chicago, IL, USA}\acmPrice{15.00}\acmDOI{http://dx.doi.org/10.1145/3077257.3077271}
\acmISBN{978-1-4503-5029-7/17/05}

\begin{document}

\setlength{\belowdisplayskip}{3pt} \setlength{\belowdisplayshortskip}{3pt}
\setlength{\abovedisplayskip}{3pt} \setlength{\abovedisplayshortskip}{3pt}
\setlength{\belowcaptionskip}{-10pt}
\selectfont

\newcommand{\cond}{\textrm{pred}\xspace}
\newcommand{\dataset}{data set\xspace}
\newcommand{\datasets}{data sets\xspace}
\newcommand{\spview}{\textsf{SPView}\xspace}
\newcommand{\fjview}{\textsf{FJView}\xspace}
\newcommand{\aggview}{\textsf{AggView}\xspace}
\newcommand{\hashfunc}[1]{\textsf{hash}(#1)\xspace}
\newcommand{\hashop}{\textsf{hash}\xspace}
\newcommand{\nsc}{\textsf{NormalizedSC}\xspace}
\newcommand{\rsc}{\textsf{RawSC}\xspace}

\newcommand{\avgfunc}{\ensuremath{\texttt{avg} }\xspace}
\newcommand{\maxfunc}{\ensuremath{\texttt{max} }\xspace}
\newcommand{\minfunc}{\ensuremath{\texttt{min} }\xspace}
\newcommand{\histfunc}{\ensuremath{\texttt{histogram\_numeric} }\xspace}
\newcommand{\countfunc}{\ensuremath{\texttt{count}}\xspace}
\newcommand{\sumfunc}{\ensuremath{\texttt{sum} }\xspace}
\newcommand{\varfunc}{\ensuremath{\texttt{var} }\xspace}
\newcommand{\stdfunc}{\ensuremath{\texttt{std} }\xspace}
\newcommand{\covfunc}{\ensuremath{\texttt{cov} }\xspace}
\newcommand{\corrfunc}{\ensuremath{\texttt{corr} }\xspace}
\newcommand{\medfunc}{\ensuremath{\texttt{median} }\xspace}
\newcommand{\percfunc}{\ensuremath{\texttt{percentile} }\xspace}
\newcommand{\havingfunc}{\ensuremath{\texttt{HAVING} }\xspace}
\newcommand{\selectfunc}{\ensuremath{\texttt{select} }\xspace}
\newcommand{\ratio}{\ensuremath{\rho }\xspace}


\newcommand{\insertion}{\ensuremath{\texttt{INSERT} }\xspace}
\newcommand{\update}{\ensuremath{\texttt{UPDATE} }\xspace}
\newcommand{\delete}{\ensuremath{\texttt{DELETE} }\xspace}

\newcommand{\sysfull}{Partition Aware Local Model\xspace}
\newcommand{\sys}{PALM\xspace}
\newcommand{\sysnospace}{PALM}

\newcommand{\tbl}[1]{\textsf{#1}\xspace}
\newcommand{\field}[1]{\textsf{#1}\xspace}
\newcommand{\cost}{\textrm{cost}\xspace}
\newcommand{\ans}{\textsf{ans}\xspace}
\newcommand{\dans}{\Delta\textsf{ans}\xspace}
\newcommand{\cqp}{correction query processing\xspace}
\newcommand{\Cqp}{Correction query processing\xspace}

\newcommand{\gray}[1]{{{\textcolor{lightgray}{\{#1\}}}\xspace}}
\newcommand{\ewu}[1]{{{\textcolor{red}{\{ewu: #1\}}}\xspace}}
\newcommand{\reminder}[1]{{{\textcolor{magenta}{\{\{\bf #1\}\}}}\xspace}}
\newcommand{\specialcell}[2][c]{%
  \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}

\def\ojoin{\setbox0=\hbox{$\bowtie$}%
  \rule[-.02ex]{.25em}{.4pt}\llap{\rule[\ht0]{.25em}{.4pt}}}
\def\leftouterjoin{\mathbin{\ojoin\mkern-5.8mu\bowtie}}
\def\rightouterjoin{\mathbin{\bowtie\mkern-5.8mu\ojoin}}
\def\fullouterjoin{\mathbin{\ojoin\mkern-5.8mu\bowtie\mkern-5.8mu\ojoin}}


\newcommand{\stitle}[1]{\vspace{0.5em}\noindent\textbf{#1}}


%\setlength{\belowcaptionskip}{-10pt}

%\newcommand{\reminder}[1] {}

%\input{coverletter.tex}

%\title{ActiveClean: Progressive Data Cleaning For Convex Data Analytics}
%\title{Towards Machine Learning Model Explanations That Are Useful For Debugging}
\title{\sys: Machine Learning Explanations For Iterative Debugging}

%\numberofauthors{2}


\author{Sanjay Krishnan}
\affiliation{\institution{UC Berkeley}}
\email{sanjaykrishnan@berkeley.edu}

\author{Eugene Wu}
\affiliation{\institution{Columbia University}}
\email{ewu@cs.columbia.edu}


%\fontsize{9pt}{11pt}
%\selectfont




\begin{abstract}
Emerging applications for machine learning in computer vision and natural language processing are using ever more complex and high-dimensional models.
To effectively debug such applications,  we argue that developers need a form of data provenance, namely, where they can isolate a small set of training examples that explain why a new example was predicted in a certain way.
Linking a prediction to responsible training data allows a data scientist to look for inconsistencies between training and test data, and understand the structure of a complex model.
The challenge is that in most models are coupled in nature where every training example contributes to a prediction in some way.
We present \sysfull (\sys), which approximates a complex model (e.g., a deep neural network) using a two-part surrogate model: a meta-model that partitions the training data, and a set of sub-models that approximate the patterns within each partition.
The user can use \sys to guide data exploration to identify problematic examples in the training dataset.
Queries to \sys are nearly 30x faster than nearest neighbor queries for identifying relevant data, which is a key property for interactive applications.
\end{abstract}

\maketitle

\pagenumbering{gobble}


\input{introduction.tex}
\input{framework.tex}
\input{algorithm.tex}
\input{interface.tex}
\input{teaser.tex}
\input{relatedwork.tex}

%\input{problem_statement.tex}
%\input{architecture.tex}
%\input{naive.tex}
%\input{detector.tex}
%\input{sampling.tex}
%\input{estimator.tex}
%\input{optimal.tex}
% \input{detect.tex}

% \input{impestimate.tex}

%\input{optimizer.tex}
%\input{experiments.tex}
%\input{relatedwork.tex}
%\input{discussion.tex}
%\input{conclusion.tex}
%\input{outlier.tex}
%\input{analysis.tex}
%\input{experiments.tex}
%\input{conclusion.tex}


%\bibliographystyle{abbrv}
%\scriptsize

\vspace{0.5em}
\noindent \textbf{Acknowledgements: }
This research was supported in part by a seed grant from the UC Berkeley Center for Information Technology in the Interest of Society (CITRIS), the UC Berkeley RISELab, and by the U.S. National Science Foundation under Award IIS-1227536: Multilateral Manipulation by Human-Robot Collaborative Systems. This work has been supported in part by funding from Google and and Cisco.


%\fontsize{8.8pt}{9.9pt} \selectfont
\bibliographystyle{ACM-Reference-Format}
\bibliography{ref,explainability} 
\normalsize \selectfont
%\appendix
%\input{appendix.tex}

\end{document}
